---
title: "Clubhouse Report"
subtitle: "July 2024"
author: "Rick Gilmore W3TM"
format: 
  revealjs:
    slide-number: true
    footer: "NARC Mtg 2024-07-09"
    logo: img/NARC-logo.png
    chalkboard: true
    multiplex: true
---

---

```{r}
url <- "https://nittany-amateur-radio-club.github.io/presentations/2024-07-09-clubhouse-rpt"
code <- qrcode::qr_code(url)
plot(code)
```

## Clubhouse report

:::: {.columns}
::: {.column width="50%"}
- [NARC-1](https://nittany-amateur-radio-club.github.io/clubhouse/narc1.html)
- [NARC-2](https://nittany-amateur-radio-club.github.io/clubhouse/narc2.html)
:::

::: {.column width="50%"}
```{r}
#| fig-cap: "<https://nittany-amateur-radio-club.github.io/clubhouse>"
url <- "https://nittany-amateur-radio-club.github.io/clubhouse"
code <- qrcode::qr_code(url)
plot(code)
```
:::
::::

## [NARC-1](https://nittany-amateur-radio-club.github.io/clubhouse/narc1.html)

- ICOM IC-7610 160-6m 100 W transceiver
- Elecraft KPA-1500 amplifier with ATU
- PC with dual monitors
- ICOM SM-30 desk mic
- Footswitch
- Full [software suite](https://nittany-amateur-radio-club.github.io/clubhouse/narc2.html#software-summary)

## [NARC-2](https://nittany-amateur-radio-club.github.io/clubhouse/narc2.html)

- [FlexRadio Flex 6400M](https://nittany-amateur-radio-club.github.io/clubhouse/flex-6400M.html) 160-6m 100 W transceiver
- Elecraft KPA-1500 amplifier with ATU
- PC with dual monitors
- Yaesu desk mic
- Footswitch
- Full [software suite](https://nittany-amateur-radio-club.github.io/clubhouse/narc2.html#software-summary)

## New developments

- Rotating Yagis!
  - [Green Heron rotator controllers](https://www.greenheronengineering.com/product/rotator-controller-rt-21/) for Mosely antennas (20m-10m)
  - Controller server for NARC1 and NARC2 (thanks, K0LO)
- New logging software ([ACLog](https://www.n3fjp.com/aclog.html) by N3FJP)
  - N3LI spearheading

---

- New [Halibut Electronics](https://electronics.halibut.com/product-category/ham/hhi) for NARC1: [Contest Controller](https://electronics.halibut.com/product/hhi-contesting-console/), [Radio Pro](https://electronics.halibut.com/product/hhi-radio-pro/)

## Coming soon...

- Work day(s)
  - Replace feedlines
  - Install 40m/80m fan dipoles
  - Install 160m dipole
  - Take down 80m-10m EFHW antenna
