---
title: "For the love of coax"
subtitle: "How to choose, how to make"
author: "Rick Gilmore W3TM"
date: "`r Sys.time()`"
output: 
  ioslides_presentation:
    css: css/ioslides-wide.css
    widescreen: true
    incremental: false
    transition: default
  html_document:
    widescreen: true
params:
  update_google_sheet: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = "center",
                      out.width = "90%")
```

## Agenda

- Choosing coax types
- Making coax patch cables

# Choosing coax

## Considerations

- Power
- Frequency
- Length, location, & use
- Connectors

## Power

- High power vs. low
- QRP

## Frequency

- HF
- VHF
- UHF or higher

## Length, location & use

- Long (e.g., feedline) vs. short (patch)
- Indoors
    - Short radius turns?
- Outdoors
    - Water resistance
    - UV resistance
    - Weight (EFHW vs. dipole)
    
## Basic principles

- Don't exceed power handling capacity
- Minimize signal loss (attenuation)
- Minimize cost
- "As short as possible"

## Some data

```{r echo=FALSE}
library(tidyverse)

if (params$update_google_sheet) {
  googledrive::drive_auth(email = "rick.o.gilmore@gmail.com")
  googledrive::drive_download(file = "coax-properties",
                              "csv/coax_properties.csv",
                              overwrite = TRUE)
}

coax <-
  readr::read_csv("csv/coax_properties.csv", show_col_types = FALSE)
```

<https://docs.google.com/spreadsheets/d/14FFnRm2fk9u0FUJHsBTqYPRzI6EGs8cr6EH4aVEpFCo/edit?usp=sharing>

---

```{r fig-loss-freq-hf-uhf, fig.cap="Attenuation (dB/100') by frequency (HF - UHF)", echo=FALSE}
coax %>%
  ggplot() +
  aes(x = freq_mhz, y = db_loss_100ft, shape=comparison, color=type) +
  geom_point() +
  geom_line() +
  theme(legend.position = "none")
```

---

```{r fig-loss-freq-hf, fig.cap="Attenuation (dB/100') by frequency: HF + 50 MHz", echo=FALSE}
coax %>%
  dplyr::filter(., freq_mhz < 100) %>%
  ggplot() +
  aes(x = freq_mhz, y = db_loss_100ft, shape=comparison, color=type) +
  geom_point() +
  geom_line() +
  theme(legend.position = "none")
```

---

```{r fig-loss-freq-hf-legend, out.height = "75%", fig.cap="Attenuation (dB/100') by frequency: HF + 50 MHz", echo=FALSE}
coax %>%
  dplyr::filter(., freq_mhz < 100) %>%
  ggplot() +
  aes(x = freq_mhz, y = db_loss_100ft, shape=comparison, color=type) +
  geom_point() +
  geom_line() +
  theme(legend.position = "bottom", legend.title = element_blank())
```

---

```{r fig-power-capacity-hf, fig.cap="Power capacity by frequency: HF + 50 MHz", echo=FALSE}
coax %>%
  dplyr::filter(., freq_mhz < 100) %>%
  dplyr::filter(., !is.na(power_capacity_watts)) %>%
  ggplot() +
  aes(x = freq_mhz, y = power_capacity_watts, shape=comparison, color=type) +
  geom_point(position = position_jitter(width = .7)) +
  geom_line() +
  theme(legend.position = "none")
```

---

```{r fig-power-capacity-hf-legend, out.height = "75%", fig.cap="Power capacity by frequency: HF + 50 MHz", echo=FALSE}
coax %>%
  dplyr::filter(., freq_mhz < 100) %>%
  dplyr::filter(., !is.na(power_capacity_watts)) %>%
  ggplot() +
  aes(x = freq_mhz, y = power_capacity_watts, shape=comparison, color=type) +
  geom_point(position = position_jitter(width = .7)) +
  geom_line() +
  theme(legend.position = "bottom", legend.title = element_blank())
```

---

```{r fig-coax-dollars-per-foot, fig.cap="Cost (US$/ft) vs. Attenuation", out.height="75%"}
coax %>%
  dplyr::filter(., freq_mhz < 100) %>%
  dplyr::filter(., !is.na(dollars_per_ft)) %>%
  ggplot() +
  aes(x=dollars_per_ft, y = db_loss_100ft, shape=comparison, color=type) +
  geom_point() +
  theme(legend.position = "bottom", legend.title = element_blank())
```

## Conclusions

- HF + 50 MHz
    - Low power
        - In shack: RG-58 or RG-8X
        - Outside/feedline: RG-58 (shorter runs) or RG-8X or RG-8U/RG-213
    - Higher power
        - In shack: RG-8U/RG-213
        - Outside/feedline: RG-8U/RG-213 or LMR-400

## Resources

- <https://www.onallbands.com/coaxial-cable-guide-understanding-the-differences-among-types-of-coaxial-cable%EF%BB%BF/>
- <https://www.qsradio.com/coax-and-connector-info.html>
- <https://www.universal-radio.com/catalog/cable/coaxperf.html>
- <https://messi.it/en/comparison-chart-50-ohm-cables.htm>

---

- <https://static.dxengineering.com/global/images/chartsguides/d/dxe-400max_ks.pdf>
- <https://www.hamradioschool.com/post/coaxial-loss-t9b05>

# Making patch cables

## What

- Coax
- Connectors (usually 2x male, but YMMV)
    - Specific to **coax type**
    - Specific to **attachment type**: solder vs. crimp/solder
- Crimp tool (if crimping), solder + soldering iron (for both)
- Cutting/prep tool (optional, but handy)

---

- Side cutters (for trimming braid)
- Heat shrink + heat gun or tape (optional but advised)

## Why?

- Fun
- Learn new skill
- Save $
    - Pre-made: [$28.99 (3')](https://www.dxengineering.com/parts/dxe-8xdx003) - [$30.49 (6')](https://www.dxengineering.com/parts/dxe-8xdx006)
    - Pay for tool cost in about 3 cables

## How

<iframe width="560" height="315" src="https://www.youtube.com/embed/IbKMiteF0_o" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe>

---

<iframe width="560" height="315" src="https://www.youtube.com/embed/QNmyGA9LHes" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe>

---

<iframe width="560" height="315" src="https://www.youtube.com/embed/nSANFhlIhMg" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe>

---

<iframe width="560" height="315" src="https://www.youtube.com/embed/N8uygjMlZ1Y" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe>

## Shopping list

- Coax
    - RG-8X <https://www.dxengineering.com/parts/dxe-8x>

----

- Connectors (PL-259/UHF Male)
    - Crimp/solder type <https://www.dxengineering.com/parts/dxe-pl259cs8x-6>
    - Solder type
        - Connector <https://www.dxengineering.com/parts/dxe-pl259-6>
        - RG-8X reducer <https://www.dxengineering.com/parts/dxe-ug176s-6/part-type/coaxial-connectors>

---

- Cutting/prep tool
    - Crimp/solder connector type <https://www.dxengineering.com/parts/dxe-ut-240c-p1>
    - Solder connector type <https://www.dxengineering.com/parts/dxe-ut-808x>
